Title

### 2021-05-11 paper/main.tex
Added probable subsections
Added refs file

%\usepackage{epstopdf}
\usepackage{epstopdf}
\author{Mateo Barría-Urenda, José Antonio Gárate}
\title{Title}
\date{}

@@

@@

@@

@@

@@

\bibliography{~/Documents/org/refs.bib}
\bibliographystyle{plainnat}

>>>>

%\usepackage{epstopdf}
\usepackage{epstopdf}
\author{Mateo Barria-Urenda, José Antonio Gárate}
\title{Title}
\date{}

@@

% Context

First synthesized in 2004 \cite{Novoselov_2004}, graphene has since
experienced an explosive growth in interest \cite{Randviir_2014}.
For pristine graphene, it's interactions with other particles are
mainly due to Van der Waals forces and $\pi-\pi$ stacking. \cite{Zuo_2012}
As pristine graphene is chemically inert \cite{Eftekhari_2017} a
classical description of it is expected to suffice in simulations.
Multiple studies on the interactions between proteins and graphene
have been published (TODO citation).

% Need

% Task

% Work

@@

\subsection{Well Tempered Multiple Walk Metadynamics}

@@

\subsection{Quantum Mechanics / Molecular Mechanics}

@@

\subsection{Adsorption Energy}

\subsection{Diffusion}

@@

\bibliography{refs.bib}
\bibliographystyle{plainnat}
